Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
remove final verify stage from list
minor change to A's CT proof
Modification of the abstract

\begin{abstract}
This work presents a sound and automated approach to synthesize 
digital feedback control architectures for physical plants represented 
as linear, time invariant models. Models are encompassed by dynamical 
equations with inputs, evolving over a continuous state space and accounting 
for errors due to the digitalization of signals that are manipulated by the 
controller block. The approach is divided in two main parts, brought together 
by a counter-example guided inductive synthesis (CEGIS) loop, as follows. 
First, we devise a static feedback controller that stabilizes the system; 
then, we verify its potential safety by means of either of the following 
approaches: forward reachability analysis via unfolding of the dynamics, 
or invariant set generation via abstract acceleration;  further, if the 
above step fails, we loop back and invoke a CEGIS call to seek alternative 
stabilizing feedback, benefiting from the obtained counterexamples 
to safety. Both approaches are able to efficiently synthesize stable and 
safe controllers considering a set of intricate physical plant models taken 
from the digital control literature.
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

>>>>

\begin{abstract}
This work presents a sound and automated approach to synthesize 
safe digital feedback controllers for physical plants represented 
as linear, time invariant models. Models are described as dynamical 
equations with inputs, evolving over a continuous state space and accounting 
for errors due to the digitalization of signals that are manipulated by the 
controller block. 
The approach works in two stages, leveraging the use of counter-example guided
inductive synthesis (CEGIS) and reachability analysis. The former synthesises a static 
feedback controller that stabilizes the system under some restrictions given by the safety of
the reach space. The latter verifies its potential safety by means of either of the following 
approaches: forward reachability analysis via unfolding of the dynamics or invariant set 
generation via abstract acceleration; if the 
verification step fails, we loop back to seek an 
alternative controller benefiting from the obtained counterexamples 
to safety using solution generalization and abstraction refinement.
We are able to efficiently synthesize stable and safe controllers
considering a set of intricate physical plant models taken from the digital
control literature.
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}
